Figure: the scatterblob

### 2022-03-31 R/scatterblob.Rmd
some edits

```{r}
library(readr)
scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

View(scatterblob_data)

```

>>>>

```{r}
# library(readr)
# scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

View(scatterblob_data)
```
